---
title: "Macaws SDM"
author: "Renata Diaz"
date: "11/20/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

## Maxent models

#### Response plots: 
```{r load maxent models}
me_models <- list.files('models/present/', 
                        pattern = 'me_', full.names = T)
for(i in 1:length(me_models)) {
  load(me_models[i])
}

dismo::response(me_b001, main = 'Beta = 0.01')
dismo::response(me_b01, main = 'Beta = 0.1')
dismo::response(me_b05, main = 'Beta = 0.5')
dismo::response(me_b09, main = 'Beta = 0.9')

rm(me_b001)
rm(me_b01)
rm(me_b05)
rm(me_b09)

rm(me_models)
```

#### Boyce's criterion

Correlation coefficient for each model: 

```{r load boyce}
boyces <- list.files('models/present', pattern = 'boyce', 
                     full.names = T)

for(i in 1:length(boyces)) {
  load(boyces[i])
}
boyce_coeff <- list()

boyce_coeff[[1]] <- boyce_b001$Spearman.cor
boyce_coeff[[2]] <- boyce_b01$Spearman.cor
boyce_coeff[[3]] <- boyce_b05$Spearman.cor
boyce_coeff[[4]] <- boyce_b09$Spearman.cor

names(boyce_coeff) <- c('beta0.01', 'beta0.1', 'beta0.5', 'beta0.9')

boyce_coeff

rm(boyce_coeff)
rm(list = c('boyce_b001', 'boyce_b01', 'boyce_b05', 'boyce_b09'))
```



The model with high beta (0.9) has the highest correlation coefficient, although it's worth noting that all of the models perform well and they generate qualitatively similar response plots.


Further analyses done using the model with beta = 0.9.

## Future predictions

#### RCP 26 (less extreme climate change scenario)

```{r load RCP 26s}

load('predictions/rcp26_2050.Rdata')
load('predictions/rcp26_2070.Rdata')

raster::plot(rcp26_2050_pred, main = 'RCP 26 - 2050')
raster::plot(rcp26_2070_pred, main = 'RCP 26 - 2070')

```

#### RCP 85 (more extreme climate change scenario)
```{r load RCP 85s}

load('predictions/rcp85_2050.Rdata')
load('predictions/rcp85_2070.Rdata')

raster::plot(rcp85_2050_pred, main = 'RCP 26 - 2050')
raster::plot(rcp85_2070_pred, main = 'RCP 26 - 2070')

```